The \project{unRAVE} catalog

### 2016-09-06 article/unrave.tex
Add JBH
Caution at the start and end of the joining-the-models section that what we have done is totally unjustified in any probabilistic sense, and it is merely a heuristic

% RAVE builders
\author{Brad K. Gibson}
% E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom.

@@

We have derived labels for all \Nspectra\ \rave\ spectra using the three models
described in previous sections.  The results from the joint model --- that includes 
the main-sequence, sub-giant and red giant branch --- shows that a single 3-label quadratic
model is too simple for the \rave\ spectral range.  The other models have problems,
too: unrealistic over-densities in label space show that the main-sequence model and
the giant model make very poor extrapolations for stars outside their respective
training sets.  For these reasons we were forced to exclude or severely penalize 
incorrect results from both models.

@@

Our catalog now contains entries of $XXX$ stars with effective temperature $\teff$,
surface gravity $\logg$, iron abundance [Fe/H], and $XXX$ of those stars are giants
with elemental abundances of [O/H], [Al/H], [Mg/H], [Ca/H], [Si/H], and [Ni/H].
In total, this leads to a catalog of X.XX million stellar abundances. 
The weighted $\teff$ and $\logg$ values for stars meeting different
S/N constraints are shown in Figure \ref{fig:test-set-hrd}, both in logarithmic density
and mean metallicity.  The artefacts from individual models are no longer 
apparent, and the rich structure of the Hertzsprung-Russell is visible.

>>>>

% RAVE builders
\author{Brad K. Gibson, Joss Bland-Hawthorn}
% E.A. Milne Centre for Astrophysics, University of Hull, Hull, HU6 7RX, United Kingdom.

@@

We have derived labels for all \Nspectra\ \rave\ spectra using the three models
described in previous sections.  The results from the joint model --- that includes 
the main-sequence, sub-giant and red giant branch --- shows that a single 3-label quadratic
model is too simple for the \rave\ spectral range.  The other models have problems,
too: unrealistic over-densities in label space show that the main-sequence model and
the giant model make very poor extrapolations for stars outside their respective
training sets.  For these reasons we were forced to exclude or severely penalize 
incorrect results from both models.  We emphasize that the choices here are entirely
heuristic, and depart from interpreting \thaecannon\ output labels as the maxima
of individual likelihood functions.  Each model produces estimates of the labels
for a given star, and we use those estimates to produce a unified estimate, but 
this is done by disregarding any probabilistic justification.

@@

Our catalog now contains entries of $XXX$ stars with effective temperature $\teff$,
surface gravity $\logg$, iron abundance [Fe/H], and $XXX$ of those stars are giants
with elemental abundances of [O/H], [Al/H], [Mg/H], [Ca/H], [Si/H], and [Ni/H].
In total, this leads to a catalog of X.XX million stellar abundances. 
The weighted $\teff$ and $\logg$ values for stars meeting different
S/N constraints are shown in Figure \ref{fig:test-set-hrd}, both in logarithmic density
and mean metallicity.  The artefacts from individual models are no longer 
apparent, and the rich structure of the Hertzsprung-Russell is visible.  Despite
this, there are a number of caveats introduced by the choices we have made to
combine estimates from multiple models. We discuss these issues in detail in
Section \ref{sec:discussion}.
